Revisiting divisible, injective and flabby abelian groups from a constructive point of view

### 2022-09-29 slides-fischbachau2022.tex
Introducing the eventually quantifier

\usepackage{graphbox}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{stmaryrd,wasysym}
\usepackage{bussproofs}
\usepackage{xspace}
\usepackage{amssymb}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{tabto}
\usepackage{xstring}
\usepackage{ifthen}
\usepackage[normalem]{ulem}
\usepackage[all]{xy}
\xyoption{rotate}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,shapes.callouts,shapes.arrows,patterns,fit,backgrounds,decorations.pathmorphing,positioning}
\hypersetup{colorlinks=true}

@@

  \normalsize
\end{frame}

>>>>

\usepackage{graphbox}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{stmaryrd,wasysym}
\usepackage{bussproofs}
\usepackage{proof}
\usepackage{xspace}
\usepackage{amssymb}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{tabto}
\usepackage{xstring}
\usepackage{ifthen}
\usepackage[normalem]{ulem}
\usepackage[all]{xy}
\xyoption{rotate}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,shapes.callouts,shapes.arrows,patterns,fit,backgrounds,decorations.pathmorphing,positioning}
\hypersetup{colorlinks=true}

@@

  \normalsize
  \pause

  \emph{* higher-order proofs of first-order statements using the assumption \\
  that a given (perhaps uncountable) set is countable}
\end{frame}

\begin{frame}{A quantifier for finite approximations}
  By a \hil{finite approximation} to an infinite sequence~$\alpha : \NN \to X$,
  we mean a \hil{finite prefix} of~$\alpha$. Notation:

  \begin{itemize}
    \item empty list $[]$
    \item extension $[x_1,\ldots,x_n] ::^r x_{n+1} = [x_1,\ldots,x_n,x_{n+1}]$
    \item we write~``$\tau \preceq \sigma$'' iff~$\tau$ is
  a refinement of~$\sigma$: $[x_1,\ldots,x_n,x_{n+1},x_{n+m}] \preceq
  [x_1,\ldots,x_n]$
  \end{itemize}
  \justifying

  For monotone predicates~$P$ of finite lists, we introduce
  a new quantifier~$\nabla$ such that~``$\nabla (\tau \preceq \sigma)\_
  P(\tau)$'' expresses that \hil{no matter how~$\sigma$ evolves to a
  better approximation~$\tau$, eventually~$P(\tau)$ will hold}.
  \[
    \infer[{\text{\scriptsize$(\sigma \in X^*)$}}]{\nabla (\tau \preceq \sigma)\_ P(\tau)}{P(\sigma)}
    \qquad
    \infer[{\text{\scriptsize$(\sigma \in X^*)$}}]{\nabla (\tau \preceq \sigma)\_ P(\tau)}{\forall(x \in X)\_\ \nabla(\tau
    \preceq (\sigma ::^r x))\_ P(\tau)}
  \]
  \[
    \infer[{\text{\scriptsize$(\sigma \in X^*, a \in X)$}}]{\nabla(\tau \preceq \sigma)\_ P(\tau)}{\forall(\tau \preceq \sigma)\_\
    a \in \tau \Rightarrow \nabla(\upsilon \preceq \tau)\_ P(\upsilon)}
  \]
\end{frame}
